---
title: "SMARTAR-tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SMARTAR-tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

SMARTAR package is for primary data analysis for sequential multiple assignment randomization trial (SMART) and are calibration tools for clinical trial planning purposes. This is a simple illustration of SMARTAR package. It only contains five main functions which are `seqmeans`, `atsmeans`, `smartest`, `smartsize` and `getncp`. In addition, it also contains one dataset `codiacs`.

The use of these functions and dataset is:

## load package and dataset

```{r setup}
library(SMARTAR)
data(codiacs)
```

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## seqmeans

Exports treatment sequence, summarizes all the sequence-specific descriptive statistics and graphs, and provides design diagram of SMART.

```{r}
seqmeans(data=codiacs ,family="gaussian",plot="d", digits = 2,xlab = "SMART design")
seqmeans(data=codiacs ,plot="s",color = "lightblue",xlab = "SEQ",family="gaussian")
```

## atsmeans

Exports all the ATS embedded in SMART design and gives estimated strategy values and the variance-covariance matrix of estimated values.

```{r}
atsmeans(data=codiacs,conf=TRUE, alpha=0.05,plot=TRUE,digits = 2,pch=18,xlab="Treatment sequence")
atsmeans(data=codiacs,conf=TRUE, alpha=0.05,digits = 2,pch=18,xlab="abc")
```

## smartest

Exports results of statistical tests of comparing adaptive treatment strategies based on both global and pairwise tests.

```{r}
smartest(data=codiacs,method="IPW",adjust="Bon")
```

## getncp

Return the value of non-centralized parameter for the chi-square distribution.

```{r}
getncp(df=5, alpha = 0.05, beta = 0.2, d = 1e-04, start = 5)
```

## smartsize

Exports estimated strategy-specified means and their confidence interval, as well as the asymptotic variance-covariance matrix for these estimates.

```{r}
smartsize(delta=0.0435,df=5,global=TRUE,alpha=0.05,beta=0.20)

SEQ <- 1:8
A1 <- c(rep(0,4),rep(1,4))
PI1 <- rep(0.5,8)
O2 <- rep(c(0,0,1,1),2)
P2 <- c(0.7,0.7,0.3,0.3,0.6,0.6,0.4,0.4)
A2 <- rep(c(0,1),4)
PI2 <- rep(0.5,8)
MEAN <- 1:8
SD <- rep(10,8)
SIMatrix <- as.data.frame(cbind(SEQ,A1,PI1,O2,P2,A2,PI2,MEAN,SD))
  
smartsize(SIMatrix,global=TRUE,alpha=0.05,beta=0.20)
```


